### 2013-11-07 doc/draft.tex
init touatex

    We shall use the type |glue_ratio| for such proportionality ratios.
    A glue ratio should take the same amount of memory as an
    |integer| (usually 32 bits) if it is to blend smoothly with \TeX's
    other data structures. Thus |glue_ratio| should be equivalent to
    |short_real| in some implementations of \PASCAL. Alternatively,
    it is possible to deal with glue ratios using nothing but fixed-point
    arithmetic; see {\sl TUGboat \bf3},1 (March 1982), 10--27. (But the
    routines cited there must be modified to allow negative glue ratios.)
    @^system dependencies@>
94. 内存耗尽
    @ If memory is exhausted, it might mean that the user has forgotten
    a right brace. We will define some procedures later that try to help
    pinpoint the trouble.
95. 是否需要加入方向属性？
    @d is_char_node(#) == (#>=hi_mem_min)
      {does the argument point to a |char_node|?}
    @d font == type {the font code in a |char_node|}
    @d character == subtype {the character code in a |char_node|}
96. TeX82 Memory Structure
97. new_param_glue 参数化glue
    new_glue 匿名glue
    new_skip_param 以上二者合体
98. penalty控制断行分页
    @ A |penalty_node| specifies the penalty associated with line or page
    breaking, in its |penalty| field. This field is a fullword integer, but
    the full range of integer values is not used: Any penalty |>=10000| is
    treated as infinity, and no break will be allowed for such high values.
    Similarly, any penalty |<=-10000| is treated as negative infinity, and a
    break will be forced.

>>>>

    We shall use the type |glue_ratio| for such proportionality ratios.
    A glue ratio should take the same amount of memory as an
    |integer| (usually 32 bits) if it is to blend smoothly with \TeX's
    other data structures. Thus |glue_ratio| should be equivalent to
    |short_real| in some implementations of \PASCAL. Alternatively,
    it is possible to deal with glue ratios using nothing but fixed-point
    arithmetic; see {\sl TUGboat \bf3},1 (March 1982), 10--27. (But the
    routines cited there must be modified to allow negative glue ratios.)
    @^system dependencies@>
94. 内存耗尽
    @ If memory is exhausted, it might mean that the user has forgotten
    a right brace. We will define some procedures later that try to help
    pinpoint the trouble.
95. 是否需要加入方向属性？
    @d is_char_node(#) == (#>=hi_mem_min)
      {does the argument point to a |char_node|?}
    @d font == type {the font code in a |char_node|}
    @d character == subtype {the character code in a |char_node|}
96. TeX82 Memory Structure
97. new_param_glue 参数化glue
    new_glue 匿名glue
    new_skip_param 以上二者合体
98. penalty控制断行分页
    @ A |penalty_node| specifies the penalty associated with line or page
    breaking, in its |penalty| field. This field is a fullword integer, but
    the full range of integer values is not used: Any penalty |>=10000| is
    treated as infinity, and no break will be allowed for such high values.
    Similarly, any penalty |<=-10000| is treated as negative infinity, and a
    break will be forced.
99. explicit kern
    明确的，直接的 3989
100. Uniscribe
     http://blogs.msdn.com/b/murrays/archive/2010/01/12/special-capabilities-of-a-math-font.aspx
     http://www.cnblogs.com/geniusvczh/archive/2012/11/06/2757868.html
     http://msdn.microsoft.com/en-us/library/windows/desktop/dd374096%28v=vs.85%29.aspx
     http://msdn.microsoft.com/zh-cn/goglobal/bb688099
     http://www.tfsattic.com/codearc/windows/UnisSample.html
     http://www.catch22.net/tuts/introduction-uniscribe
     http://maxradi.us/documents/uniscribe/
     http://www.microsoft.com/typography/developers/uniscribe/intro.htm
     http://blog.csdn.net/jianlizhao66/article/details/1480748
101. eexec Encryption，Type1字体的加密
102. `T1ascii' translates a PostScript Type 1 font from compact binary (PFB) to
      ASCII (PFA) format. The result is written to the standard output unless an
      OUTPUT file is given.
103. PASCAL的ord函数：ord('a')=97, chr(7)。加上x之后用户编码处理
     @d null_code 0
     @d carriage_return 015
     @d invalid_code 0177
104. 字符串处理，TeX中所有的字符串都存储在str_pool中
105. memory_word是分段的，是有固定数目的。
106. Lyle Ramshaw于1980年设计了TFM文件。
     JFM是将character code转换成了character type。
107. new_character 这就是要分析的。
108. 注意XeTeX中的：
     function new_native_word_node(f:internal_font_number; n:integer): pointer;
     function new_native_character(f:internal_font_number; c:UnicodeScalar): pointer;
     procedure font_feature_warning
     procedure font_mapping_warning
     procedure do_locale_linebreaks (s:integer; len:integer);
109. DVI导言区的内容
     i[1] DVI类型
     num[4] den[4] 整数
     mag[4] 缩放
110. http://wiki.apache.org/xmlgraphics-fop/GoogleSummerOfCode2006/FloatsImplementationProgress/ImplementingBeforeFloats
     http://tex.loria.fr/english/texbib.html
     http://dl.acm.org/citation.cfm?id=865455
270
